Measurement of deeply virtual Compton scattering off Helium-4

### 2020-01-08 eg6-letters/long-paper/prc-dvcshelium.tex
Add intro and refs (with an unresolved issue)

@@

\begin{acknowledgments}
 Put your acknowledgments here.
\end{acknowledgments}

% Create the reference section using BibTeX:
\bibliography{basename of .bib file}

>>>>

The developpement of the three dimensional structure functions to study the nucleon 
in the past decades is the opportunity to revisit the quark structure of the nucleus
with this new perspective. This new approach to the structure of the nucleus in terms 
of quarks and gluons is particularly needed as it remains today the subject of numerous
controvercies. Indeed, while much progress has been made in measuring the nuclear
parton distribution functions (PDFs) and in particular the EMC effect \cite{}. The 
observed shape of the distribution remains fundamentaly unexplained, in particular
in the intermediate $x$ range, where are observed the anti-shadowing and the EMC 
effects \cite{}.

In particular, the generalized parton distributions (GPDs) can be probed through
spin assymetries in the deeply virtual Compton scattering (DVCS) process in a very 
convenient way. Moreover, on nuclear targets of spin-0, the extraction can be 
simplified with the reduction of the number of GPDs. The measurement of the nuclear
DVCS is however a challenging task, first attempts from the HERMES collaboration 
\cite{} did not lead to important progress, but more recent measurements from the
CLAS collaboration \cite{} have been much more promising. We extend in this article 
the description of the nuclear DVCS CLAS experiment, detail the methods used for the
measurement and publish for the first time the full results for each channel measured.

@@

\begin{acknowledgments}
	% Add Sergio and ERC!
 Put your acknowledgments here.
\end{acknowledgments}

% Create the reference section using BibTeX:
\bibliography{hadro.bib}
